A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-07-27 survey.tex
Fixing some typos

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ square of pixels, also known as build tiles. Although the
resolution of walkable areas is in squares of $8 \times 8$ pixels, also known as walk tiles. The typical dimensions for maps range from $64 \times 64$ to $256 \times 256$ build tiles. Each player  can
control up  to 200 units (plus an unlimited number of buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  most of them with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals ($E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively), the best StarCraft AI bots are ranked between $D$ and $D^+$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

@@

% CBR:
Also falling into the machine-learning category, a significant group of researchers has explored case-based reasoning (CBR) \cite{Aamodt94CBR} approaches for strategic decision making. For example Aha et al. \cite{LTW} used CBR to perform dynamic plan retrieval in the Wargus domain. Hsieh and Sun \cite{HsiehS08} based their work on Aha et al.'s CBR model \cite{LTW} and used StarCraft replays to construct states and building sequences (``build orders''). Schadd et al. \cite{SchaddBS07} applied a CBR approach to opponent modeling through hierarchically structured models of the opponent behavior and they applied their work to the Spring RTS game (a ``Total Annihilation'' clone). Finally, \v{C}ertick\'{y} et al. \cite{certicky2013cbr} used CBR to build their army based on the opponent's army composition and they pointed the importance of a proper scouting for better results.

>>>>

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ squares of pixels, also known as build tiles. Although the
resolution of walkable areas is in squares of $8 \times 8$ pixels, also known as walk tiles. The typical dimensions for maps range from $64 \times 64$ to $256 \times 256$ build tiles. Each player  can
control up  to 200 units (plus an unlimited number of buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  most of them with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals ($E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively), the best StarCraft AI bots are ranked between $D$ and $D^+$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

@@

% CBR:
Also falling into the machine-learning category, a significant group of researchers has explored case-based reasoning (CBR) \cite{Aamodt94CBR} approaches for strategic decision making. For example Aha et al. \cite{LTW} used CBR to perform dynamic plan retrieval in the Wargus domain. Hsieh and Sun \cite{HsiehS08} based their work on Aha et al.'s CBR model \cite{LTW} and used StarCraft replays to construct states and building sequences (``build orders''). Schadd et al. \cite{SchaddBS07} applied a CBR approach to opponent modeling through hierarchically structured models of the opponent behavior and they applied their work to the Spring RTS game (a ``Total Annihilation'' clone). Finally, \v{C}ertick\'{y} et al. \cite{certicky2013cbr} used CBR to build their army, based on the opponent's army composition, and they pointed out on the importance of proper scouting for better results.
